### 2020-06-01 paper.tex
Add Conclusion Section (Paper is Finished)

Insert conclusion and future work here

>>>>

This paper presented a new algorithm for solving the cell placement problem that combines simulated annealing and genetic algorithms by enhancing the population used in the genetic algorithm. After checking the results, it's concluded that the proposed algorithm shows better results compared to running each algorithm independently especially when the specified population size is comparatively small. As the population size increases, the solutions of the proposed implementation approach to those generated from running a genetic algorithm with randomly generated populations. It is also presumed from table \ref{table4} that at relatively large population sizes, genetic algorithms may show better results, but with a negligible margin of improvement nevertheless.
For future work, it's planned to broaden the implementation of the simulation program for better flexibility with various inputs which would lead to more in-depth tests.
